Functional Enrichment Tests: Intro and methods comparison

### 2023-07-10 DRAFT_Funct_Enrich.Rmd
cleaning up annotation

```{r setup, include=FALSE}
#library(tidyverse)
```

@@

@@

```{bash}
perl -e '$count=0; $len=0; while(<>) {s/\r?\n//; s/\t/ /g; if (s/^>//) { if ($. != 1) {print "\n"} s/ |$/\t/; $count++; $_ .= "\t";} else {s/ //g; $len += length($_)} print $_;} print "\n"; warn "\nConverted $count FASTA records in $. lines to tabular format\nTotal sequence length: $len\n\n";' \
DRAFT_Funct_Enrich/annot/GCF_002022765.2_C_virginica-3.0_translated_cds.faa > DRAFT_Funct_Enrich/annot/GCF_002022765.2_C_virginica-3.0_translated_cds.tab
```

```{bash}
head -1 DRAFT_Funct_Enrich/annot/GCF_002022765.2_C_virginica-3.0_translated_cds.tab
```

@@

join blast with cdsftab

```{r}
g.spid <- left_join(blast, cdsftab, by = "V1") %>%
  mutate(gene = str_extract(V2.y, "(?<=\\[gene=)\\w+")) %>%
  select(gene, V11, V2.x) %>%
  mutate(SPID = str_extract(V2.x, "(?<=\\|)[^\\|]*(?=\\|)")) %>%
  distinct(gene, SPID, .keep_all = TRUE)
```

>>>>

```{r setup, include=FALSE}
library(tidyverse)
```

@@

This protein fasta is used as query for blast of uniprot_sprot database.

@@

```{r engine='bash', eval=TRUE}
perl -e '$count=0; $len=0; while(<>) {s/\r?\n//; s/\t/ /g; if (s/^>//) { if ($. != 1) {print "\n"} s/ |$/\t/; $count++; $_ .= "\t";} else {s/ //g; $len += length($_)} print $_;} print "\n"; warn "\nConverted $count FASTA records in $. lines to tabular format\nTotal sequence length: $len\n\n";' \
DRAFT_Funct_Enrich/annot/GCF_002022765.2_C_virginica-3.0_translated_cds.faa > DRAFT_Funct_Enrich/annot/GCF_002022765.2_C_virginica-3.0_translated_cds.tab
```

```{r engine='bash', eval=TRUE}
head -1 DRAFT_Funct_Enrich/annot/GCF_002022765.2_C_virginica-3.0_translated_cds.tab
```

@@

Now we can take the two data frames: A) blast output of taking protein fasta and comparing to uniprot_swiss-prot and B) a tabular version of same fasta file that has ID numbers of importance. Note this importance was determined based on what we want to use down stream.

```{r, eval=TRUE}
g.spid <- left_join(blast, cdsftab, by = "V1") %>%
  mutate(gene = str_extract(V2.y, "(?<=\\[gene=)\\w+")) %>%
  select(gene, V11, V2.x) %>%
  mutate(SPID = str_extract(V2.x, "(?<=\\|)[^\\|]*(?=\\|)")) %>%
  distinct(gene, SPID, .keep_all = TRUE)
```
